---
extype: string
exsolution: NA
exname: rethink2m6
expoints: 1
categories:
- probability
- bayes
- bayes-grid
- rethink-chap2
- string
date: '2023-10-30'
slug: Rethink2m6
title: Rethink2m6

---



```{r libs, include = FALSE}
library(tidyverse)
library(gt)
```


```{r global-knitr-options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H',
                      fig.asp = 0.618,
                      fig.width = 4,
                      fig.cap = "", 
                      fig.path = "",
                      message = FALSE,
                      warning = FALSE,
                      out.width = "100%",
                      cache = TRUE)
```








# Aufgabe

This question is taken from McElreath, R. (2020). *Statistical rethinking: A Bayesian course with examples in R and Stan* (2. Ed.). Taylor and Francis, CRC Press.


2M6. Imagine that black ink is heavy, and so cards with black sides are heavier than cards with white sides. As a result, it’s less likely that a card with black sides is pulled from the bag. So again assume there are three cards: B/B, B/W, and W/W. After experimenting a number of times, you conclude that for every way to pull the B/B card from the bag, there are 2 ways to pull the B/W card and 3 ways to pull the W/W card. Again suppose that a card is pulled and a black side appears face up. Show that the probability the other side is black is now 0.5. Use the counting method, as before.


</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>

# Lösung


Let's label the cards *bb* (black on both sides), *bw* (black on one, white on the other), and *ww* (both sides are white), respectively.

Wanted is the probability that the *second* side of the card is black (*2b*), *given* one side is already identified as black (*1b*): $Pr(2b|1b)$.


Bayes-Box to the rescue:

```{r echo = FALSE}
d <-
  tibble::tribble(
  ~Hyp, ~Prior,
  "bb",     1L, 
  "bw",     2L,   
  "ww",     3L, 
  ) %>% 
  mutate(Likelihood = c(2,1,0),
         unstand_post = Prior*Likelihood,
         std_post = unstand_post / sum(unstand_post))
```


Whenever the probability of all paths (in a tree diagram) is the same, we do not need to write down the probability of the path for the likelihood. It is enough to write the number of paths.

```{r echo = FALSE}
d %>% 
  gt::gt()
```





---

Categories: 

- probability
- bayes
- bayes-grid
- rethink-chap2
- string

