---
extype: string
exsolution: NA
exname: rethink2m5
expoints: 1
categories:
- probability
- bayes
date: '2022-10-26'
slug: Rethink_2m5
title: Rethink_2m5

---



```{r libs, include = FALSE}
library(tidyverse)
library(gt)
```


```{r global-knitr-options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H',
                      fig.asp = 0.618,
                      fig.width = 4,
                      fig.cap = "", 
                      fig.path = "",
                      message = FALSE,
                      warning = FALSE,
                      out.width = "100%",
                      cache = TRUE)
```








# Exercise

This question is taken from McElreath, R. (2020). *Statistical rethinking: A Bayesian course with examples in R and Stan* (2. Ed.). Taylor and Francis, CRC Press.


2M5. Now suppose there are four cards: B/B, B/W, W/W, and another B/B. Again suppose a card is drawn from the bag and a black side appears face up. Again calculate the probability that the other side is black.



</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>

# Solution

The only difference to the question 2M4 is that we now have two *bb* cards, rendering the *prior* plausibility twice as high.

Let's label the cards *bb* (black on both sides), *bw* (black on one, white on the other), and *ww* (both sides are white), respectively.

Wanted is the probability that the *second* side of the card is black (*2b*), given one side is black (*1b*): $Pr(2b|1b)$.



```{r}
d <-
  tibble::tribble(
  ~Hyp, ~Prior,
  "bb",     2L, 
  "bw",     1L,   
  "ww",     1L, 
  ) %>% 
  mutate(Likelihood = c(2,1,0),
         unstand_post = Prior*Likelihood,
         std_post = unstand_post / sum(unstand_post))

```

```{r echo = FALSE}
d %>% 
  gt() %>% 
  fmt_number(columns = 5)
```


The following solution is taken from [this source](https://sr2-solutions.wjakethompson.com/bayesian-inference.html).


```{r}
card_bb_likelihood <- 2
card_bw_likelihood <- 1
card_ww_likelihood <- 0

likelihood <- c(card_bb_likelihood, card_bw_likelihood, card_ww_likelihood,
                card_bb_likelihood)
prior <- c(1, 1, 1, 1)
posterior <- likelihood * prior
posterior <- posterior / sum(posterior)

posterior[1] + posterior[4]


```





---

Categories: 

- probability
- bayes

