---
extype: string
exsolution: NA
exname: rethink2m3
expoints: 1
categories:
- probability
- bayes
date: '2022-10-24'
slug: Rethink_2m3
title: Rethink_2m3

---



```{r libs, include = FALSE}
library(tidyverse)
```


```{r global-knitr-options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H',
                      fig.asp = 0.618,
                      fig.width = 4,
                      fig.cap = "", 
                      fig.path = "",
                      message = FALSE,
                      warning = FALSE,
                      out.width = "100%",
                      cache = TRUE)
```








# Exercise

This question is taken from McElreath, R. (2020). *Statistical rethinking: A Bayesian course with examples in R and Stan* (2. Ed.). Taylor and Francis, CRC Press.


2M3. Suppose there are two globes, one for Earth and one for Mars. The Earth globe is 70% covered in water. The Mars globe is 100% land. Further suppose that one of these globes—you don’t know which—was tossed in the air and produced a “land” observatiion. Assume that each globe was equally likely to be tossed. Show that the posterior probability that the globe was the Earth, conditional on seeing “land” (Pr(Earth|land)), is 0.23.




</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>

# Solution

Zur Erinnerung:

$$\begin{aligned}
Pr(A) &= Pr(A \cap B) + Pr(A \cap A^C)  \qquad \text{| bei disjunkten Ereignissen}\\
Pr(A \cap B) &= Pr(A|B) \cdot Pr(B)\\
Pr(A \cap B^C) &= Pr(A|B^C) \cdot Pr(B^C)
\end{aligned}$$



Wobei  $A^C$ das komlementäre Ereignis zu $A$ meint.

The solution is taken from [this source](https://sr2-solutions.wjakethompson.com/bayesian-inference.html).



```{r}
# probability of land, given Earth:
p_le <- 0.3

# probability of land, given Mars:
p_lm <- 1.0

# probability of Earth:
p_e <- 0.5

# prob. of Mars:
p_m <- 0.5

# probability of land:
# das ist die Summe zweier gemeinsamer Wahrscheinlichkeiten (Randwahrscheinlichkeit)
# also die Summe zweier Zellen aus der Kontingenztabelle
p_l <- (p_e * p_le) + (p_m * p_lm)


# probability of Earth, given land (using Bayes' Theorem):
p_el <- (p_le * p_e) / p_l
p_el
#> [1] 0.231


```





---

Categories: 

- probability
- bayes

