---
exname: kekse01
extype: num
exsolution: r .6
exshuffle: no
extol: 1
expoints: 1
categories:
- probability
- bayes-grid
date: '2022-10-26'
slug: kekse02
title: kekse02

---






```{r global-knitr-options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H',
                      fig.asp = 0.618,
                      fig.width = 4,
                      fig.cap = "", 
                      fig.path = "",
                      echo = FALSE,
                      message = FALSE,
                      fig.show = "hold")
```






# Exercise

In *Think Bayes* stellt Allen Downey folgende Aufgabe:


"Next let's solve a cookie problem with 101 bowls:

Bowl 0 contains 0% vanilla cookies,

Bowl 1 contains 1% vanilla cookies,

Bowl 2 contains 2% vanilla cookies,

and so on, up to

Bowl 99 contains 99% vanilla cookies, and

Bowl 100 contains all vanilla cookies.

As in the previous version, there are only two kinds of cookies, vanilla and chocolate. So Bowl 0 is all chocolate cookies, Bowl 1 is 99% chocolate, and so on.

Suppose we choose a bowl at random, choose a cookie at random, and it turns out to be vanilla. What is the probability that the cookie came from Bowl $x$, for each value of $x$?"

Hinweise:

- Untersuchen Sie die Hypothesen $\pi_0 = 0, \pi_1 = 0.1, \pi_2 = 0.2, ..., \pi_{10} = 1$ für die Trefferwahrscheinlichkeit
- Erstellen Sie ein Bayes-Gitter zur Lösung dieser Aufgabe.
- Gehen Sie davon aus, dass Sie (apriori) indifferent gegenüber der Hypothesen zu den Parameterwerten sind.
- Geben Sie Prozentzahlen immer als Anteil an und lassen Sie die führende Null weg (z.B. .42).


</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>

# Solution


```{r}
#| message: false
library(tidyverse)
```


```{r}
d <-
  tibble(
    # definiere die Hypothesen (das "Gitter"): 
    p_Gitter = 0:100 / 101,
    # bestimme den Priori-Wert:       
    Priori  = 1) %>%  
    mutate(
      # berechne Likelihood für jeden Gitterwert:
      Likelihood = p_Gitter,
      # berechen unstand. Posteriori-Werte:
      unstd_Post = Likelihood * Priori,
      # berechne stand. Posteriori-Werte (summiert zu 1):
      Post = unstd_Post / sum(unstd_Post))  
```

```{r}
#| echo: false
d %>% 
  knitr::kable(digits=2)
```


```{r}
ggplot(d) +
  aes(x = p_Gitter, y = Post) + 
  geom_line()
```







---

Categories: 

- probability
- bayes-grid

