---
exname: mtcars-simple3
extype: num
exsolution: 512
exshuffle: yes
extol: 0.1
expoints: 1
categories:
- regresssion
- en
- bayes
- frequentist
- qm1
- stats-nutshell
date: '2022-09-04'
slug: mtcars-simple3
title: mtcars-simple3

---




```{r libs, include = FALSE}
library(tidyverse)
#library(glue)
options(mc.cores = parallel::detectCores())

```


```{r global-knitr-options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H',
                      fig.asp = 0.618,
                      fig.width = 4,
                      fig.cap = "", 
                      fig.path = "",
                      echo = TRUE,
                      message = FALSE,
                      fig.show = "hold")
```






# Exercise

We will use the dataset `mtcars` in this exercise.

Assume your causal model of your research dictates that fuel economy is a linear function of horse power, cylinder count and displacement of the engine.

*Which of the predictors in the above model has the weakest causal impact on the output variable?*


Notes:

- Use can either use frequentist or bayesian modeling.
- Use R for all computations.
- There are multiple ways to find a solution.


Answerlist
----------
* `cyl`
* `hp`
* `disp`
* All are equally strong
* none of the above






</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>

# Solution

```{r message=FALSE}
library(rstanarm)
library(easystats)
library(tidyverse)
```


In order to gauge the relative importance of the predictors,
we need to make sure they are on the same scale:


```{r}
mtcars2 <-
  standardise(mtcars)
```


Compute Model:

```{r}
lm1_freq <- lm(mpg ~ hp + cyl + disp, data = mtcars2)
lm1_bayes <- stan_glm(mpg ~ hp + cyl + disp, data = mtcars2, refresh = 0)
```


Get parameters:


```{r}
parameters(lm1_bayes)
```

Note that the absolute value of the coefficient's estimate is what we are after.

The predictors with the strongest impact is `disp`, and `cyl`. 
The weakest influence has `hp`.



Answerlist
----------


* wrong
* correct
* wrong
* wrong
* wrong





---

Categories: 

- regresssion
- en
- bayes
- frequentist
- qm1
- stats-nutshell

