---
date: 2024-03-11
draft: FALSE  
title: r-quiz 

execute: 
  eval: true 
  
highlight-style: arrow 
cache: true


number-sections: true

extype: string
exsolution: ""
exshuffle: no
categories:
- R  # ENTER CATEGORIES HERE
- en
- quiz

---





## Define a variable

:::{.panel-tabset}

## Exercise

Define in R the variable `age` and assign the value `42`.

## Solution


```{r}
age <- 42
```

Note that spaces here are not mandatory, but useful.

:::


## Define a variable as a string
:::{.panel-tabset}

## Exercise

Define in R the variable `name` and assign the value `me`.


## Solution


```{r}
name <- "me"
```
:::


## Define a variable by another variable
:::{.panel-tabset}

## Exercise

Define in R the variable `name` and assign the *variable* `age`.

## Solution 


```{r}
name <- age
```
:::

## Call a function
:::{.panel-tabset}

## Exercise
Ask R what today's  `date()` is, that is, call a function.


## Solution 


```{r}
date()
```
:::

## Define a vector
:::{.panel-tabset}
## Exercise
Define in R a vector `x` with the values 1,2,3 . 

## Solution 
```{r}
x <- c(1, 2, 3)
```
:::



## Sum up vector
:::{.panel-tabset}
## Exercise
Define in R a vector `x` with the values 1,2,3 . Then sum up its values.

## Solution 
```{r}
x <- c(1, 2, 3)
sum(x)
```
:::

## Vector wise computation
:::{.panel-tabset}
## Exercise
Square each value in the vector `x`.


## Solution

```{r}
x^2
```

:::


## Vector wise computation 2
:::{.panel-tabset}

## Exercise

Square each value in the vector `x` and sum up the values.

## Solution

```{r}
sum(x^2)
```

:::


## Compute the variance
:::{.panel-tabset}


## Exercise

Compute the variance of `x` using basic arithmetic.

## Solution

```{r}
 x <- c(1, 2, 3)

sum((x - mean(x))^2) / (length(x)-1)

 # compare: 
var(x) 
```

:::

## Work with NA
:::{.panel-tabset}


## Exercise

Define the vector `y` with the values 1,2,NA. Compute the mean. Explain the results.

## Solution

```{r}
y <- c(1, 2, NA)
mean(y)
```


`NA` (not available, ie., missing data) is contagious in R: If there's a missing element, R will assume that something has gone wrong and will raise a red flag, i.e, give you a NA back.
:::





