---
date: 2024-03-11  # HEUTIGES DATUM EINTRAGEN
draft: TRUE   # ACHTUNG DRAFT STEHT AUF TRUE!
title: r-quiz 

execute: 
  eval: true 
  
highlight-style: arrow 
cache: true


extype: string
exsolution: ""
exshuffle: no
categories:
- R  # ENTER CATEGORIES HERE
- en
- quiz

---




Question
========



:::{.panel-tabset}

## Define a variable

Define in R the variable `age` and assign the value `42`.

## Solution


```{r}
age <- 42
```

Note that spaces here are not mandatory, but useful.

:::


:::{.panel-tabset}

## Define a variable as a string

Define in R the variable `name` and assign the value `me`.


## Solution


```{r}
name <- "me"
```
:::



:::{.panel-tabset}

## Define a variable by another variable

Define in R the variable `name` and assign the *variable* `age`.

## Solution 


```{r}
name <- age
```
:::


:::{.panel-tabset}
## Call a function

Ask R what today's  `date()` is, that is, call a function.


## Solution 


```{r}
date()
```
:::


:::{.panel-tabset}
## Define a vector
Define in R a vector `x` with the values 1,2,3 . 

## Solution 
```{r}
x <- c(1, 2, 3)
```
:::




:::{.panel-tabset}
## Sum up vector
Define in R a vector `x` with the values 1,2,3 . Then sum up its values.

## Solution 
```{r}
x <- c(1, 2, 3)
sum(x)
```
:::


:::{.panel-tabset}
## Vector wise computation

Square each value in the vector `x`.


## Solution

```{r}
x^2
```

:::



:::{.panel-tabset}

## Vector wise computation 2

Square each value in the vector `x` and sum up the values.

## Solution

```{r}
sum(x^2)
```

:::



:::{.panel-tabset}


## Compute the variance

Compute the variance of `x` using basic arithmetic.

## Solution

```{r}
 x <- c(1, 2, 3)

sum((x - mean(x))^2) / (length(x)-1)

 # compare: 
var(x) 
```

:::


:::{.panel-tabset}


## Work with NA

Define the vector `y` with the values 1,2,NA. Compute the mean. Explain the results.

## Solution

```{r}
y <- c(1, 2, NA)
mean(y)
```


`NA` (not available, ie., missing data) is contagious in R: If there's a missing element, R will assume that something has gone wrong and will raise a red flag, i.e, give you a NA back.
:::





