---
extype: string
exsolution: NA
exname: rethink2e4
expoints: 1
categories:
- probability
- philosophy
date: '2022-10-24'
slug: Rethink_2E4
title: Rethink_2E4

---



```{r libs, include = FALSE}
library(tidyverse)
```


```{r global-knitr-options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H',
                      fig.asp = 0.618,
                      fig.width = 4,
                      fig.cap = "", 
                      fig.path = "",
                      message = FALSE,
                      warning = FALSE,
                     # out.width = "100%",
                      cache = TRUE)
```








# Exercise

This question is taken from McElreath, R. (2020). *Statistical rethinking: A Bayesian course with examples in R and Stan* (2. Ed.). Taylor and Francis, CRC Press.


2E4. The Bayesian statistician Bruno de Finetti (1906–1985) began his 1973 book on probability theory with the dedication: “PROBABILITY DOES NOT EXIST.” The capitals appeared in the original, so I imagine de Finetti wanted us to shout this statement. What he meant is that probability is a device for describing uncertainty from the perspective of an observer with limited knowledge; it has no objective reality. Discuss the globe tossing example from the chapter, in light of this statement. What does it mean to say “the probability of water is 0.7”?


</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>

# Solution

The solution is taken from [this source](https://sr2-solutions.wjakethompson.com/bayesian-inference.html).


The idea is that probability is only a subjective perception of the likelihood that something will happen. 
In the globe tossing example, the result will always be either “land” or “water” (i.e., 0 or 1). 
When we toss the globe, we don’t know what the result will be, but we know it will always be “land” or “water.” 
To express our uncertainty in the outcome, we use probability. 
Because we know that water is more likely than land, we may say that the probability of “water” is 0.7; however, we’ll never actually observe a result of 0.7 waters, or observe any probability. We will only ever observe the two results of “land” and “water.”




---

Categories: 

- probability
- philosophy

