---
extype: string
exsolution: NA
exname: rethink2m1
expoints: 1
categories:
- probability
- bayes-grid
- rethink-chap2
- string
date: '2023-11-08'
slug: Rethink2m1
title: Rethink2m1

---



```{r libs, include = FALSE}
library(tidyverse)
```


```{r global-knitr-options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H',
                      fig.asp = 0.618,
                      fig.width = 4,
                      fig.cap = "", 
                      fig.path = "",
                      message = FALSE,
                      warning = FALSE,
                     # out.width = "100%",
                      cache = TRUE)
```








# Aufgabe

This question is taken from McElreath, R. (2020). *Statistical rethinking: A Bayesian course with examples in R and Stan* (2. Ed.). Taylor and Francis, CRC Press.


2M1. Recall the globe tossing model from the chapter. Compute and plot the grid approximate posterior distribution for each of the following sets of observations. In each case, assume a uniform prior for *p*.


1. WWW
2. WWWL
3. LWWLWWW



</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>

# Lösung

The solution is taken from [this source](https://sr2-solutions.wjakethompson.com/bayesian-inference.html).


```{r}
library(tidyverse)

dist <- 
  tibble(
    # Gridwerte bestimmen:
    p_grid = seq(from = 0, to = 1, length.out = 20),
    # Priori-Wskt bestimmen:
    prior = rep(1, times = 20)) %>%
  mutate(
    # Likelihood berechnen:
    likelihood_1 = dbinom(3, size = 3, prob = p_grid),  # WWW
    likelihood_2 = dbinom(3, size = 4, prob = p_grid),  # WWWL
    likelihood_3 = dbinom(5, size = 7, prob = p_grid),  # LWWLWWW
    # unstand. Posterior-Wskt:
    unstand_post_1 = likelihood_1 * prior,
    unstand_post_2 = likelihood_2 * prior,
    unstand_post_3 = likelihood_3 * prior,
    # stand. Post-Wskt:
    std_post_1 = unstand_post_1 / sum(unstand_post_1),
    std_post_2 = unstand_post_2 / sum(unstand_post_2),
    std_post_3 = unstand_post_3 / sum(unstand_post_3)
    ) 
```

Hier ist die Bayes-Box:

```{r}
knitr::kable(round(dist, 2))
```



Jetzt können wir das jeweilige Diagramm zeichnen:


```{r}
library(ggpubr)
ggline(dist,
       x = "p_grid",
       y = "std_post_1")
```


Oder mit `ggplot2`:


```{r}
ggplot(dist) +
  aes(x = p_grid, y= std_post_1) +
  geom_line()+
  geom_point() +
  labs(x = "p(W)",
       y = "Posteriori-Wahrscheinlichkeit",
       title = "Daten: WWW")

ggplot(dist) +
  aes(x = p_grid, y= std_post_2) +
  geom_line()+
  geom_point() +
  labs(x = "p(W)",
       y = "Posteriori-Wahrscheinlichkeit",
       title = "Daten: WWWL")

ggplot(dist) +
  aes(x = p_grid, y= std_post_3) +
  geom_line()+
  geom_point() +
  labs(x = "p(W)",
       y = "Posteriori-Wahrscheinlichkeit",
       title = "Daten: LWWLWWW")
```




---

Categories: 

- probability
- bayes-grid
- rethink-chap2
- string

