---
extype: string
exsolution: NA
exname: rethink2m7
expoints: 1
categories:
- probability
- bayes
date: '2022-10-26'
slug: Rethink_2m7
title: Rethink_2m7

---



```{r libs, include = FALSE}
library(tidyverse)
library(gt)
```


```{r global-knitr-options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H',
                      fig.asp = 0.618,
                      fig.width = 4,
                      fig.cap = "", 
                      fig.path = "",
                      message = FALSE,
                      warning = FALSE,
                      out.width = "100%",
                      cache = TRUE)
```








# Exercise

This question is taken from McElreath, R. (2020). *Statistical rethinking: A Bayesian course with examples in R and Stan* (2. Ed.). Taylor and Francis, CRC Press.


2M7. Assume again the original card problem, with a single card showing a black side face up. 
Before looking at the other side, 
we draw another card from the bag and lay it face up on the table. 
The face that is shown on the new card is white. 
Show that the probability that the first card, the one showing a black side, 
has black on its other side is now 0.75. Use the counting method, if you can. 
Hint: Treat this like the sequence of globe tosses, 
counting all the ways to see each observation, for each possiible first card.


</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>
</br>

# Solution

Let's label the cards *bb* (black on both sides), *bw* (black on one, white on the other), and *ww* (both sides are white), respectively.

To keep things straigt, here's visualization of our data

```{r echo=FALSE}
d <-
  tibble(id = c(1,3),
         color = c("black", "white"),
         label = c("card 1", "card 2"))

d %>% 
  ggplot(aes(x = id)) +
  geom_rect(aes(xmin = id, ymin = 0, xmax = id + 1, ymax = 2, fill = color), color = "grey80") + 
  ggpubr::theme_transparent() +
  theme(panel.background = element_rect(fill = "grey40")) +
  scale_fill_manual(values = d$color) +
  geom_label(y = .5, aes(label = label, x = id+.5)) +
  guides(fill = FALSE)
  
  
```


Wanted is the probability $Pr(c1=bb|1b,2w)$, the probability of drawing (as card 1) a *bb*  card, given that we observerd b in the first draw, denoted as *1b*, and a white card in the second draw, denoted as *2w*.


Let's draw a tree diagram for easier comprehension.


```{r, echo = FALSE, out.width="100%"}
DiagrammeR::mermaid("graph TD
  A[Start] -->B[_b_b]
  E ---M[valid]
  A -->C[b_b_]
  A -->D[_b_w]
  B -->E[_w_w]
  B -->F[w_w_]
  F --- N[valid]
  B -->K[_b_w]
  K ---O[invalid]
  C -->G[_w_w]
  G ---P[valid]
  C -->H[w_w_]
  H ---Q[valid]
  C -->L[_b_w]
  L ---R[invalid]
  D -->I[_w_w]
  I ---S[valid]
  D -->J[w_w_]
  J ---T[valid]
  ")

```

In the diagram, the symbol "_b_w" means that *b*lack face of a the bw-card (one black, one white face) was drawn. 
Similarly, "_b_b" means that one (of the two) *b*lack faces of the bb-card (two black faces) was drawn.


Here, we have to consider two cards. Let's use this notation *ww-bb* for the sequence "first card is white on both sides, second card is black on both sides".

The data observed is: first card has one black side, the second card has one white side, i.,e *b-w*.



Looking at the tree, we realize that out of all 8  paths, 6 feature the *bb* card as first card:

$Pr(1bb|1b,2w) = 6/8 = 3/4 = 0.75$

where `c1` means "card 1", and `b-w` means "first draw showed a *b* side, and second card showed a *w* face".


As a Bayes-Grid (or "Bayes-Box") we can depict the situation like this:

```{r echo=FALSE}

tibble::tribble(
  ~Hyp, ~Prior, ~L, ~unstand_Post, ~Post,
  "bb",     2L, 3L,            6L, "3/4",
  "bw",     1L, 2L,            2L, "1/4"
  ) %>% 
  knitr::kable()
```

Or, using probability, and not counts:

```{r echo=FALSE}
tibble::tribble(
  ~Hyp, ~Prior, ~L, ~unstand_Post, ~Post,
  "bb",     2L, "3/4",           "6/4", "3/4",
  "bw",     1L, "2/4",            "2/4", "1/4"
  ) %>% 
  knitr::kable()
```



---

Categories: 

- probability
- bayes

